From Freebase to Wikidata: The Great Migration

### 2015-10-07 paper.tex
Reworked Section 3.2.

The second challenge is that the Wikidata community is very interested to have references
for their statements, sources that Freebase usually did not store except for
some specific data like populations and unemployment rates.
For these two specific cases we have just kept the references from Freebase.
In order to provide the Wikidata community with references for the facts in Freebase
we have reused data from the Knowledge Vault, another Google project with the aim
to extract facts from the web (see~\cite{dong2014knowledge}).
Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
the references from often do not meet the requirement for a~good reference:
they include pages in social networks, shopping sites, filesharers, \emph{etc.}
It became necessary to filter and curate the references before inclusion in Wikidata.

>>>>

The second challenge is that the Wikidata community is very eager to have references
for their statements, \emph{i.e.}, sources that Freebase usually did not store,
except for some specific data like populations and unemployment rates.
For these two specific cases, we have just kept the references from Freebase.
In order to provide the Wikidata community with references for the facts in Freebase,
we have reused data from another Google research project
called Knowledge Vault~\cite{dong2014knowledge} aimed at extracting facts from the Web.
Whereas the fact extraction was usually correct, the pages Knowledge Vault extracted
the references from often do not meet the Wikidata requirements for reliable references:
they include pages in social networks, shopping sites, file sharing hosters, \emph{etc.}
It became necessary to filter the references before potential inclusion in Wikidata
by introducing a~domain blacklist.%
\footnote{URL blacklist:
\url{https://www.wikidata.org/wiki/Wikidata:Primary_sources_tool/URL_blacklist}}
